Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity

### 2022-01-21 paper.tex
Minor Query R9: Added [Using equation 6 ...] to text.

Prior to the onset of either instability, the flux tube is found to be linearly
unstable to perturbations of the form~\eqref{eq:kink_perturbation} at $t=20$
via Suydam's criterion~\eqref{eq:suydams_criterion}
(Figure~\ref{fig:suydam_condition_4}). The criterion represents a balance
between destabilising pressure gradients and stabilising magnetic shear and in
this case, the shear is so small and the pressure gradient so large that the
tube is unstable over a wide range of radii, for $ 0.02 \lessapprox
r \lessapprox 0.29$. The measure of linear fluting growth rate $\gamma$ is
plotted as a function of $r$ at the same time (Figure~\ref{fig:growth_rate_4}).
The location of the peak growth matches nearly exactly the location of the
resonant surface where the observed perturbation grows
(Figure~\ref{fig:swi-4_pressure_13}) and an estimate of the linear growth rate
can be found by averaging $\gamma$ over $r$, giving a growth rate of $0.86$.

>>>>

Prior to the onset of either instability, the flux tube is found to be linearly
unstable to perturbations of the form~\eqref{eq:kink_perturbation} at $t=20$
via Suydam's criterion~\eqref{eq:suydams_criterion}
(Figure~\ref{fig:suydam_condition_4}). The criterion represents a balance
between destabilising pressure gradients and stabilising magnetic shear and in
this case, the shear is so small and the pressure gradient so large that the
tube is unstable over a wide range of radii, for $ 0.02 \lessapprox
r \lessapprox 0.29$. \rev{Using
  equation~\eqref{eq:fluting_growth_rate2}, the} linear
fluting growth rate $\gamma$ is plotted as a function of $r$ at the
same time 
(Figure~\ref{fig:growth_rate_4}).

The location of the peak growth matches nearly exactly the location of the
resonant surface where the observed perturbation grows
(Figure~\ref{fig:swi-4_pressure_13}) and an estimate of the linear growth rate
can be found by averaging $\gamma$ over $r$, giving a growth rate of $0.86$.
